\huge Modeling Intervention Strategies for TB Control in the United States

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
still working on poster

@@

@@

@@

@@

              \caption{The Hill Model}

@@

@@

            describe the dynamics of the model for the FB population. 

@@

>>>>

        \vspace{-3em}

@@

                N             &= S(t) + I(t) + R(t)\\

@@

        \vspace{-2em}

@@

          \begin{column}{.2\textwidth}

@@

              \caption{A flow chart representing the compartments of the Hill
                       Model.}

@@

          \begin{column}{.6\textwidth}

@@

            describe the dynamics of the model for the FB population. Further,
            each compartment in this model also loses people to do natural
            death. The system of differential equations for this model is
            naturally more complex and is provided in an appendix. In order to
            implement this model, Hill, Becerra, and Castro used the \texttt{R}
            programming language, with the \texttt{lsoda} routine to numerically
            solve the differential equations. 

@@

        For this implementation, various numerical solvers were implemented,
        including an Eulerian Method, a Quadratic Method, a Fourth-order runge
        kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
        model was implemented, further tracking capabilities were added as well
        as economic modeling. This implementation tracks total active TB cases,
        entering cases of LTBI, and treatment costs for active and latent disease
        for all populations. Tracking was used to evaluate various interventions
        explored in Hill, Becerra, and Castro's work, as well as interventions
        exploring the possibility of treating incoming LTBI cases.
